\documentclass[a4paper,10pt]{article}

\usepackage[left=0.6in,right=0.6in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=15pt}

\titleformat{\section}{\bfseries\uppercase}{ }{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\begin{document}

\begin{center}
{\LARGE \textbf{Shailendra Kumar Yadav}}\\
Ujjain, +91 8817044936, shailendraky2004@gmail.com
\end{center}

\section*{EDUCATION}

\textbf{Bachelor of Technology in Computer Science (AI, ML)}, GLA University, Mathura \hfill June 2026\\
7.3 CGPA

\textbf{Intermediate}, Aditya Birla Public School, Nagda \hfill May 2022\\
81\%

\textbf{High School}, Aditya Birla Public School, Nagda \hfill May 2020\\
80\%

\section*{EXPERIENCE}

\textbf{AI Engineer}, Watermelon Software \hfill 15 Oct 2025 -- Present
\begin{itemize}
\item Working on production-level AI chatbot handling millions of logs and real-time user interactions.
\item Designing scalable LLM-based systems with optimized prompt pipelines and vector databases.
\item Implementing AI-driven automation and integrating advanced NLP technologies in live environments.
\end{itemize}

\textbf{AI/ML Intern}, Bharat Tech, Lucknow \hfill May 2024 -- November 2024
\begin{itemize}
\item Trained and deployed NLP models for the CollegeCue platform (summarization and semantic search).
\item Fine-tuned transformer models using Hugging Face on domain-specific datasets.
\item Integrated models into backend systems using Python.
\end{itemize}

\textbf{Job Oriented Value-Added Course}, GLA University, Mathura \hfill June 2024 -- July 2024\\
\textit{Trainee}
\begin{itemize}
\item Learned ML fundamentals and completed a mini project “Exam Evaluation”.
\end{itemize}

\section*{PROJECTS}

\textbf{AI-Based Exam Evaluator} \hfill June 2024 -- July 2024
\begin{itemize}
\item Built automated evaluation system for theoretical and OMR exams using OpenCV and PIL.
\item Enabled fast and accurate grading with AI-based processing.
\item Tech: OpenCV, PIL, AI, ML.
\end{itemize}

\textbf{Credit Risk Model} \hfill Feb 2025 -- Apr 2025
\begin{itemize}
\item Built ML pipeline to predict delinquent borrowers with feature engineering and model tuning.
\item Improved targeting using Random Forest.
\item Tech: Python, Sklearn, Pandas, NumPy.
\end{itemize}

\textbf{Smart Chatbot with LangChain} \hfill May 2025 -- Jun 2025
\begin{itemize}
\item Developed multi-LLM chatbot with LangChain and vector memory.
\item Routed domain-specific queries and retained conversational context.
\item Tech: Python, LangChain, FAISS, OpenAI API.
\end{itemize}

\section*{SKILLS}

\textbf{Technical:} Java, Python, C, JavaScript, Express.js, Machine Learning, Scikit-learn, AI Agent Development, MySQL, GitHub, LangChain, ANN, CNN, LangGraph, MongoDB, KNN, Transformer Models, Diffusion Models

\textbf{Professional:} Leadership Skills, Teamwork, Effective Communication Skills

\section*{PROFESSIONAL ACHIEVEMENTS / INSIGHTS}

\begin{itemize}
\item 2nd Prize – University Summer Project Competition.
\item Attended IBM Workshop on ML, NLP, and Data Mining.
\end{itemize}

\section*{DECLARATION}

I hereby declare that all the above-mentioned information is true and correct to the best of my knowledge.

\end{document}